Predicting Sales Level for Newly Published Books \\ using Cost-Sensitive Ensemble Methods

### 2016-12-08 paper.tex
adding new references (related to ensembles) and some sentences
working in the SoA

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
%First you have to explain why it is enough to predict the level of
%sales, and not the precise number. 
An important task when publishing a new book is determining an accurate number 
of copies to be printed. Doing both an under- or an overestimation will lead to financial losses.
In this paper, we address the problem of predicting total sales using cost-sensitive ensemble methods.
% Antonio - explain briefly what are them
These can be used as reliable decision-aid tools for publishers, as a part of the final stages of the editorial process. 
Thus, a real dataset including the complete sales data for books published in Spain across several years has been used to compute the prediction models.
% Antonio - extend a bit this with the followed methodology.
% Explain also the method you are using and why it's an improvement
% over the previous one - JJ
Results show that %\emph{EXPLAIN THE RESULTS OBTAINED}.

@@

Inside the publishing process of a new book, deciding the optimal {\em
  print run}, i.e. the number of copies to be printed and delivered to
bookstores, is a very challenging problem, that is why it is extremely
important to develop accurate predictive models which could forecast
the future sales a new book will achieve, in order to optimise
production schedules: to improve the publishing company profits and to
minimise losses \cite{Zhao2001}, due both to the excess or to the
scarcity of units. 
%I would eliminate this paragraph. We have it on the other one.
Since, according to the results reported in \cite{Fildes2010,Saeed2008}, reducing the error in estimated sales leads to an enhancement of the whole production process.

@@

%\textbf{UNDER CONSTRUCTION}
% Antonio - I remove the ';)' because I want to check the parentheses correspondence and it breaks it. :P

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
%First you have to explain why it is enough to predict the level of
%sales, and not the precise number. 
An important task when publishing a new book is determining an accurate number 
of copies to be printed. Doing both an under- or an overestimation will lead to financial losses.
In this paper, we address the problem of predicting total sales using cost-sensitive ensemble methods.
% Antonio - explain briefly what are them
These can be used as reliable decision-aid tools for publishers, as a part of the final stages of the editorial process. 
Thus, a real dataset including the complete sales data for books published in Spain across several years has been used to compute the prediction models.
% Antonio - extend a bit this with the followed methodology.
% Explain also the method you are using and why it's an improvement
% over the previous one - JJ
We evaluate our approach on the real data collected by a Spanish publishing company.
Results show that %\emph{EXPLAIN THE RESULTS OBTAINED}.

@@

Reliable sales prediction can enhance the whole production process for different companies involved in manufacturing, marketing and trading.

Specifically, focusing in the publishing process of a new book, deciding the optimal {\em
  print run}, i.e. the number of copies to be printed and delivered to
bookstores, is a very challenging problem, that is why it is extremely
important to develop accurate predictive models which could forecast
the future sales a new book will achieve, in order to optimise
production schedules: to improve the publishing company profits and to
minimise losses \cite{Zhao2001}, due both to the excess or to the
scarcity of units. 
%I would eliminate this paragraph. We have it on the other one.
Since, according to the results reported in \cite{Fildes2010,Saeed2008}, reducing the error in estimated sales leads to an enhancement of the whole production process.

@@

Sales prediction is an important problem that can improve the quality of business 
strategy for different companies. 
Traditionally, sales prediction problems have been solved using advaced methods 
such as regression models \cite{Papalexopoulos1990}, neural networks \cite{Yoo1999}, 
fuzzy systems \cite{Mastorocostas2001}, or mixture of methods \cite{Chang2006715,Meulstee2008,ChiJie2012}.

%\textbf{UNDER CONSTRUCTION}
